---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rippo

<!-- badges: start -->
<!-- badges: end -->

The goal of rippo is to ease data entry and tracking of AAGI-CU Intellectual Property and Project Outputs for reporting purposes.

## Installation

You can install the development version of rippo like so:

```r
o <- options() # store default options

options(pkg.build_vignettes = TRUE)

if (!require("pak"))
  install.packages("pak")
pak::pak("AAGI-AUS/rippo")

options(o) # reset options
```

## Running IPPO Shiny app

rippo includes a shiny web app to make interfacing with the IPPO tables simpler.
Once rippo is installed you can run the web app like so:

```{r}
library(rippo)
run_IPPO_app()
```

The app currently has the following features:
- Add background IP by specifying the relevant details.
- Add background IP from a catalogue of frequently-used IP
- Add outputs and specify links between outputs and background IP
- Add correspondance related to outputs
- Load an existing IPPO registry
- Edit and delete existing entries
- Export resulting IPPO in .xlsx format

### The background IP catalogue

The current catalogue contains a selection of IP from a small number of AAGI projects.
We do not expect this is a complete list of the frequently used IP.
If you believe there is IP that is used frequently by yourself and others and should be added to the catalogue, submit an issue with either:
- the package name and relevant language, or
- the relevant information for the IPPO table.

### Limitations on IPPO upload

While the uploader works well on IPPO iles generated using the app, older files that do not conform to the same structure can run into issues.
When uploading your existing IPPO register, be aware of the following restrictions (this list may change as further development is undertaken).

- If the description of background IP in the imported document does not match *exactly* any of the descriptions in the catalogue, it will be identified as a novel piece of IP.
This can be confusing for packages where the name may be the same but they are identified as different due to discrepencies in the description.

- Dates are expected to be formatted as date objects in excel.
If stored as text (or other) data types, this may cause issues upon loading.

- The links between outputs and background IP are expected to come as `Table X, Lines Y` where `X` is the relevant table and `Y` is a list of comma separated integers coresponding to the rows in that table.
If you have a run of consecutive rows, the app will expect each entry to be listed *individually*, not collapsed.
For example, an entry for table 1 may look like `Table 1, Lines 1,2,3,4,8` not `Table 1 Lines 1:4, 8` nor `Table 1 Lines 1-4, 8`.

## Example

This is a basic example which shows you how to solve a common problem:

```r
# create a Word document of IPPO tables from each of the project's registers

library(rippo)
create_ippo_tables()
```

## Contributions 

All contributions are appreciated, but please make sure to follow the [Contribution Guidelines](.github/CONTRIBUTING.md).

